---
output:
  html_document: default
  pdf_document: default
---
---
title: "Reproducible Research"
author: "Christopher"
date: "April 15, 2019"
output: html_document
===============================================================================
# Code for reading in the dataset
```{r processing data, echo=TRUE}
#Reading csv Data into Data.Table
activityDT <- data.table::fread(input = "data/activity.csv")
activityDT$day <- weekdays(as.Date(activityDT$date))
activityDT$DateTime <- as.POSIXct(activityDT$date,format = "%Y%M%D")
## Data without na's
clean <- activityDT[!is.na(activityDT$steps),]
```
#  Histogram of total number of steps per day
```{r hist, echo=TRUE}
totalstepsperday <- aggregate(steps ~ date,data = activityDT,FUN = sum, na.rm = FALSE)
totalstepsperday
hist(totalstepsperday$steps,breaks = 5, xlab = "steps", main = "Total Steps per Day",col = "red")
```
# Mean number of steps taken per day
```{r mean, echo=TRUE}
as.integer(mean(totalstepsperday$steps))
```
# Median number of steps taken per day
```{r median, echo=TRUE}
as.integer(median(totalstepsperday$steps))
```
# # Time series plot of the average number of steps taken
```{r time series plot, echo=TRUE}
StepsPerInterval <- tapply(activityDT$steps,activityDT$interval,mean, na.rm = TRUE)
plot(as.numeric(names(StepsPerInterval)),StepsPerInterval,xlab = "5-Minute Iterval",ylab = "Average Steps Taken", main = "Average Daily Activity Pattern", type = "l",col = "red")
```
# Maximum number of steps
```{r maximum steps}
maxInterval <- names(sort(StepsPerInterval,decreasing = TRUE)[1])
maxsteps <- sort(StepsPerInterval,decreasing = TRUE)[1]
maxsteps
```
# Calculate and report the total number of missing values in the dataset
```{r calculate and report, echo=TRUE}
nrow <- sum(is.na(activityDT$steps))
nrow
```
## Create the average number of steps per weekdays and interval
```{r missing data, echo=TRUE}
activityDT2 <- activityDT
nas <- is.na(activityDT2)
StepsPerInterval <- tapply(activityDT$steps,activityDT,mean,na.rm =TRUE)
names(activityDT2)
```
## Checking for NON NA
```{r non na, echo= TRUE}
sum(is.na(activityDT2))
```
#Creating the histogram of total steps per day catergorized by dataset
## Histogram with no NA values
```{r missing values, echo= TRUE}
StepsPerDay2 <- aggregate(steps~date, data = activityDT2, FUN = sum, na.rm = TRUE)
hist(StepsPerDay2$steps,main = StepsPerDay2,ylab = "interval",col ="red",breaks = 5)
```
# Create a new catergory based on two levels  indicating whether a given date is weekend or weekday 
## Add the new weekend/weekday field and making a new factor
```{r weekend or weekday}
activityDT2 <-data.table::fread(input ="data/activity.csv")  
activityDT2[, date := as.POSIXct(date,format = "%Y-%m-%d")]  
activityDT2[,"Day of week":= weekdays(x = date)]
activityDT2[grepl(pattern = "Monday|Tuesday|Wednesday|Thursday|Friday",x ="Day of week"),"weekday or weekend"] <- "weekday"
activityDT2[grepl(pattern = "Saturday|Sunday",x = "Day of Week"),"weekend or weekday"] <- "weekend"
head(activityDT2,10)
```
# Making a panel plot containing a time series plot
```{r}
```





